---
title: "WhiteFly"
author: "Kien TN"
date: "February 23, 2018"
output: html_document
---
<style type="text/css">
body p {
  color: #5040C7;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source('whitefly.R')
```

## Cambodia data

#### Cambodia Adult
*NOTE that for each District, we use combined data of 20 plants of both Transect A and B.  
Boxplot to show the distribution of mean per district.

```{r cmA Adult Count, echo=FALSE}
ggplot(sum_CM, aes(District, SUM_adult)) +
  geom_boxplot() + coord_flip()
```

ANOVA test to see if there any difference between means.
```{r cmA Anova}
summary(results1)
```
=> p-value is large and we fail to reject the Null Hypothesis, meaning that there is NO significant difference in district means of both Transect A and Transect B.


#### Cambodia Nymph
All are 1s. Since the data is coded, and without detail, it's hard to conduct more statistical tests.
```{r}
table(cm$Transect_A_nymph)
table(cm$Transect_B_nymph)
```


## Vietnam data

#### Vietnam Adult
Similarly to what we did with Cambodia data, here, we start with the same boxplot, then ANOVA and depending on ANOVA's result, we conduct Tukey test.   
*NOTE: we are not using data from Thuan Chau and Van Yen Districts where have fewer than 5 samples.

```{r vnA Adult Count, echo=FALSE}
ggplot(sum_VN, aes(District, SUM_adult)) +
  geom_boxplot() + coord_flip()
```

```{r vnA Anova}
summary(results3)
```
Significant p-value. = Possibilities of difference in District means. We proceed to he ad-hoc test to see where this difference is. 


The following table shows significant pairs: these are pairs of districts that have significant difference in frequency of Nymph class (p-value smaller than 0.05)
```{r vnA TukeyHSD}
kable(tukey3)
```



#### Vietnam Nymph
Because Nymph Class is Categorical data, we cannot apply Anova here. Instead, we are going to use Chi Squared test to see whether there are association between different Nymph Classes. 
```{r vnA data table}
table(vn$Transect_A_nymph)
kable(vn_AN1, caption = "Distribution of Nymph Class per District")
```


The Association Plot below is a way of visualizing the distribution table above. Coloring from Blue to Red means going from Important to Not Important. This plot packs a lot of information, the tests we're going the conduct after will break down the infomation in our data.
```{r vnA Association Plot, echo=FALSE}
assoc(vn_AN2, shade=TRUE)
```


We use Chi Squared test to see if there are association between different levels of Nymph Count (3 levels: 0 to 5, 5 to 10, and 10 to 25)
```{r vnA ChiSquared, warning=FALSE}
chisq.test(vn_AN1)
```


Because Chi Squared gave significant results, we go on to do a post-hoc test to see what District pair have significant association. This following tables tells us which pair of Districts have significant assocition of Nymph Class frequency. 
```{r vnA ChiSq post-hoc, warning=FALSE}
kable(Chisq_vnA)
```


Apply similar procedure for Transect B
```{r vnB data table}
table(vn$Transect_B_nymph)
kable(vn_BN1, caption = "Distribution of Nymph Class per District")
```

```{r vnB Association Plot, echo=FALSE}
assoc(vn_BN2, shade=TRUE)
```


We use Chi Squared test to see if there are association between different levels of Nymph Count (4 levels: 0 to 5, 5 to 10, 10 to 25, and 25 to 50)
```{r vnB ChiSquared, warning=FALSE}
chisq.test(vn_BN1)
```


Table of significant pairs
```{r vnB ChiSq post-hoc, warning=FALSE}
kable(Chisq_vnB)
```
